---
title: "lilliansoccer10_PeerCommentary_Amandafw_04"
author: "Amanda Wu"
date: "2023-10-31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Part 1

### Create Two Data Sets with Normal Distribution
```{r}
set.seed(0)
data.frame <- rnorm(50,5,1)
additional.data.frame <- rnorm(50,6,1)
```

### Create one Data Set without Normal Distribution
```{r}
baddistribution <- c(1, 2, 3, 4, 5)
baddistribution
```

### Create the Function

I am unsure of how to add code to to test (n∗p>5 and n∗(1−p)>5). Any suggestions?

```{r}
z.prop.test <- function (x, y = NULL, alternative = "two.sided", mu, sigma.x, 
    sigma.y = NULL, conf.level = 0.95) 
{
    choices <- c("two.sided", "greater", "less")
    alt <- pmatch(alternative, choices)
    alternative <- choices[alt]
   
    if (!is.null(y)) {
        dname <- paste(deparse(substitute(x)), "and", paste(deparse(substitute(y))))
    }
  
    else {
        dname <- deparse(substitute(x))
    }
    mx <- mean(x)
    estimate <- mx
  
    if (is.null(y)) {
        stderr <- sigma.x/sqrt(mx)
        zobs <- (mx - mu)/stderr
        method <- c("One-sample z-Test")
        names(estimate) <- c("mean of x")
    }
       if (is.null(sigma.y)) {
        stderr <- sigma.x/sqrt(mx)
        zobs <- (mx - mu)/stderr
        method <- c("One-sample z-Test")
        names(estimate) <- c("mean of x")
    }
    else {
        my <- mean(y)
        method <- c("Two-sample z-Test")
        estimate <- c(mx, my)
        names(estimate) <- c("mean of x", "mean of y")
        stderr <- sqrt(((sigma.x^2)/mx) + ((sigma.y^2)/my))
        zobs <- (mx - my - mu)/stderr
    }
    if (alternative == "less") {
        pval <- pnorm(zobs)
        cint <- c(NA, zobs * stderr + qnorm(conf.level) * stderr)
    }
    else if (alternative == "greater") {
        pval <- 1 - pnorm(zobs)
        cint <- c(zobs * stderr - qnorm(conf.level) * stderr, 
            NA)
    }
    else {
        pval <- 2 * pnorm(-abs(zobs))
        alpha <- 1 - conf.level
        cint <- c(zobs * stderr - qnorm((1 - alpha/2)) * stderr, 
            zobs * stderr + qnorm((1 - alpha/2)) * stderr)
    }
    cint <- cint + mu
    names(zobs) <- "z"
    if (!is.null(y)) 
        names(mu) <- "difference in means"
     if (!is.null(x)) 
        names(mu) <- "difference in means"
  
    else names(mu) <- "mean"
    attr(cint, "conf.level") <- conf.level
    rval <- list(statistic = zobs, p.value = pval, conf.int = cint, 
        estimate = estimate, null.value = mu, alternative = alternative, 
        method = method, data.name = dname)
    attr(rval, "class") <- "htest"
    return(rval)
}
```

### Test to See if The Function Works with Multiple Scenerios
```{r}
#y and sigma.y = NULL
z.prop.test(data.frame, y = NULL, alternative = "two.sided", mu = 0, sigma.x = 2, sigma.y = NULL, conf.level = 0.95) 
```

```{r}
#sigma.y = NULL
z.prop.test(data.frame, y=additional.data.frame, alternative = "two.sided", mu = 0, sigma.x = 2, sigma.y = NULL, conf.level = 0.95) 
```

```{r}
#all information included
z.prop.test(data.frame, y=additional.data.frame, alternative = "two.sided", mu = 0, sigma.x = 2, sigma.y = 3, conf.level = 0.95) 
```
Notes: Nice job with the function! Everything seemed to work but the one thing that I noticed was that your function and dataset never included the variables p1, p2, n1, n2? I had a similar function as yours but I modified it so it would include all the variables which allowed me to include the check test code (n∗p>5 and n∗(1−p)>5) with the if statements. - AW
## Part 2

```{r warning=FALSE}
library(curl)
library(ggplot2)
library(tidyverse)
```

### Import the Data Set
```{r}
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN588_Fall23/KamilarAndCooperData.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE) #Assign D as the vector for the data set
head(d)
```

### Plot the variables in a Scatterplot
```{r}
par(mfrow = c(1, 2))
plot(data=d, MaxLongevity_m ~ Brain_Size_Species_Mean)
plot(data=d, log(MaxLongevity_m) ~ log(Brain_Size_Species_Mean))
```
Notes: I think in the instructions, you're supposed to use ggplot2 to plot the scatterplots but the plots look good! - AW

### Add A Fitted Line to the Scatterplots - Determine the Intercept(B0) and Slope (B1)

```{r}
mI <- lm(MaxLongevity_m ~ Brain_Size_Species_Mean, data = d)
summary(mI)
mII <-  lm(log(MaxLongevity_m) ~ log(Brain_Size_Species_Mean), data = d)
summary(mII)
```

```{r warning=FALSE}
par(mfrow = c(1, 2))
g <- ggplot(data = d, aes(x = Brain_Size_Species_Mean, y = MaxLongevity_m))
g <- g + geom_point()
g <- g + geom_smooth(method = "lm", formula = y ~ x)
g + annotate("text", x = 150, y = 800, label = "y=1.2180x + 248.9523")
h <- ggplot(data = d, aes(x = log(Brain_Size_Species_Mean), y = log(MaxLongevity_m)))
h <- h + geom_point()
h <- h + geom_smooth(method = "lm", formula = y ~ x)
h + annotate("text", x = 2, y = 6.5, label = "y=0.23415x +  4.87895")
```
Notes: Nice job! This is pretty similar to what I had gotten too! -AW

### Identify and interpret the point estimate of the slope (β1), as well as the outcome of the test associated with the hypotheses H0: β1 = 0; HA: β1 ≠ 0. Also, find a 90 percent CI for the slope (β1) parameter.

- The estimate of the slope B1 for MaxLongevity_m ~ Brain_Size_Species_Mean is 1.2180. When B1 equals 0, y is equal to  248.9523. When B1 does not equal zero, it is the expected change in units of y for every 1 unit of change in x.

-The estimate of the slope B1 for log(MaxLongevity_m) ~ log(Brain_Size_Species_Mean) is 0.23415. When B1 equals 0, y is equal to
4.87895. When B1 does not equal zero, it is the expected change in units of y for every 1 unit of change in x.

Notes: Good explanations! - AW 
### Find a 90% Confidence Interval Based on Each B1(m) Parameter
```{r}
ciI <- confint(mI, level = 0.90)  
ciI
ciII <- confint(mII, level = 0.90)  
ciII
```
Notes: This was also what I had gotten as well -AW
### Plot the 90% CI and Predicion 
```{r warning=FALSE}
g <- ggplot(data = d, aes(x = Brain_Size_Species_Mean, y = MaxLongevity_m))
g <- g + geom_point()
g <- g + geom_smooth(method = "lm", formula = y ~ x, color = "black")
g <- g + geom_abline(intercept = 230.540738, slope = 1.035571, linewidth = 1, color = "blue")
g <- g + geom_abline(intercept = 267.36379, slope = 1.40041, linewidth = 1, color = "blue")
g + annotate("text", x = 150, y = 800, label = "y=1.2180x + 248.9523")
```
```{r warning=FALSE}
h <- ggplot(data = d, aes(x = log(Brain_Size_Species_Mean), y = log(MaxLongevity_m)))
h <- h + geom_point()
h <- h + geom_smooth(method = "lm", formula = y ~ x, color = "black")
h <- h + geom_abline(intercept = 4.7644934, slope = 0.2046396, linewidth = 1, color = "blue")
h <- h + geom_abline(intercept = 4.9934084, slope = 0.2636595, linewidth = 1, color = "blue")
h + annotate("text", x = 2, y = 6.5, label = "y=0.23415x +  4.87895") 
```

## I can't Figure out How to Make A Legend :( Any suggestions?
Notes: the lines look good! It could be helpful to include where you found the function geom_abline, just in case you may need it in the future. I was able to add a legend by using the function "legend(x-value placement, y-value placement, legend = c(the titles you want to add), fill = c(the colors for each line Ex: "black", "blue"))". This is similar to how you inserted the linear equation onto the plot. However, I didn't plot it using ggplot but rather followed the instructions from module 12 when they were plotting CI and prediction lines so it could be helpful to look there. -AW

```{r}
cipredI <- predict(mI, newdata = data.frame(Brain_Size_Species_Mean = 800), interval = "confidence",
    level = 0.90) 
cipredI
```

### I do trust the model to make that prediction because the fit was ~1223 with a 90% CI. The point is predicted to be between ~1089 and ~1357. When 800 is typed into the model equation alone y=1.2180x + 248.9523, it gets ~1223. 

Notes: This was a super hard assignment but I think you did really well! I think you definitely found more functions/code that was much shorter than mine but we still had similar answers for question 2. The only big thing was question 1 and how you might have missed one of the requirements? But also I might not be reading your code correctly or understanding your code. I think there might be a slight difference between normal z.test vs z.test for proportational data, it might be helpful to look into it further. Question 2 looks great! Your scatterplots all look correct. - AW


